---
title: "apply family"
author: "T"
date: "January 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

#lapply- is for list (input list, output list)
takes a list as input\
applies a function to each element of the list\
then returns a list of the same length as the original one.\
 
##read data and view data
```{r}
getwd()
flags <- read.table("./data/flags.txt", header = TRUE)
head(flags)
dim(flags)

```

use lapply function to loop (class) each column

```{r}
class(flags)
cls_list<- lapply(flags, class) 
cls_list
class(cls_list) #return list

```
cls_list can be simplified to a character vector. To do this manually\

```{r}
as.character(cls_list)
```

#sapply (input list, output vector or matrix)

sapply() allows you to automate this process by calling lapply() behind the scenes\

if the result is a list where every element is of length
one, then sapply() returns a vector.\

If the result is a list where
every element is a vector of the same length (> 1), sapply() returns a matrix.\

```{r}
cls_vect <- sapply(flags,class)
cls_vect
class(cls_vect)
```

create dataset only contain color
```{r}
sum(flags$orange)

flag_colors <- flags[, 11:17]

head(flag_colors)
```
sum of each column of flag_colors, call the lapply() function with two arguments\

```{r}
lapply(flag_colors,sum)
```
since lapply() always returns a list\

result can be simplified to a vector by calling sapply() instead of lapply()\

```{r}
sapply(flag_colors,sum)
```
sapply mean

```{r}
sapply(flag_colors,mean)
```
##sapply---length >1 example

sapply() has been able to simplify the result to vector. That's because each element of the list returned by lapply() was a vector of length =1.\

Recall that sapply() instead returns a matrix when each element of the list returned by lapply() is a vector of the same length (> 1)\

```{r}
flag_shapes <- flags[, 19:23]

head(flag_shapes)

lapply(flag_shapes,range) #list contain two vaule, because length >1

shape_mat <- sapply(flag_shapes,range)  #return martix because length >1
shape_mat

class(shape_mat) #return matrix
```
use lapply() to apply the unique() function to each column in the flags dataset = (unique_vals)\

Since unique_vals is a list, use sapply to determine the length of each element of unique_vals\

```{r}
unique(c(3,4,5,5,5,6,6))

unique_vals <- lapply(flags, unique)
unique_vals

sapply(unique_vals,length)
```

Use sapply() to apply the unique() function to each column of the flags=lapply in pervious

```{r}
sapply(flags, unique)
```

lapply(unique_vals, function(elem) elem[2]) will return a list
containing the second item from each element of the unique_vals list.\

Note that our function takes one argument, elem, which is just a 'dummy variable' that takes on the value of each element of unique_vals, in turn.\

```{r}
lapply(unique_vals, function(elem) elem[2])
```

