---
title: "vapply-tapply function"
author: "T"
date: "January 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Read data
```{r}
flags <- read.table("./data/flags.txt", header = TRUE)
```

Whereas sapply() tries to 'guess' the correct format of the result,
vapply() allows you to specify it explicitly.\

If the result doesn't match the format you specify, vapply() will throw an error\

The 'character(1)' argument tells R that we expect the class function to return a character vector of length 1 when applied to EACH column of the flags dataset.\

```{r}
sapply(flags, unique)



#vapply(flags, unique, numeric(1))  NOT WORK

sapply(flags, class)
vapply(flags, class, character(1))

```

As a data analyst, you'll often wish to split your data up into
groups based on the value of some variable, then apply a function to
the members of each group.\


The 'landmass' variable in our dataset takes on integer values
between 1 and 6\

Use table(flags$landmass) to see how many flags/countries fall
into each group.\


```{r}
head(flags)
table(flags$landmass)
```
Use table(flags$animate) to see how many flags contain an animate image.\

```{r}
table(flags$animate)
```

apply the mean function to the 'animate' variable separately for each of the six landmass groups\

giving us the proportion of flags containing an animate image WITHIN each landmass group.\

```{r}
tapply(flags$animate, flags$landmass, mean)
#single landmass animate/total animate
```

Similarly, we can look at a summary of population values (in round
millions) for countries with and without the color red on their flag
with tapply(flags$population, flags$red, summary).\

```{r}
tapply(flags$population, flags$red, summary)
```

use the same approach to look at a summary of population values for each of the six landmasses.\

```{r}
tapply(flags$population, flags$landmass, summary)
```

use vapply() as a safer alternative to sapply(), which is most helpful when writing your own functions.\

tapply() to split your data into groups based on the value of some variable, then apply a function to each group.\