---
title: "function"
author: "T"
date: "January 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Function

##Basic function
```{r}
x1 <- function(a){
  a*10
}
x1(9)

x2 <- function(b){
  b
}
x2('Just return')

x2 # reture function code
```

## More arguments (parameter)

```{r}
ab <- function(a,b){
  a*10

} 

ab(9)
```

##Create a mean function

```{r}

my_mean <- function(my_vector) {
  my_vector=sum(my_vector)/length(my_vector) 
}
mm <- my_mean(c(2,3,4))
mm #turn value
mean(c(2,3,4))
```
## argument with value

```{r}
remainder <- function(num, divisor = 2) {
  num%%divisor
   
}
remainder(3)

remainder(11,5) # give value 5 to divisor and arguments have been matched

remainder(divisor = 11, num = 5) # If designate argument values by name, the ordering of the argument will not that impoart

remainder(7, div = 3) #partially match arguments

args(remainder) # show the arguments for this function 



```
## evaluate data--alternative way to do samething 

if a function is passed into the
"func" argument and some data (like a vector) is passed into the dat argument
the evaluate() function will return the result of dat being passed as an
argument to func.\

```{r}


# Hints: This exercise is a little tricky so I'll provide a few example of how
# evaluate() should act:
#    1. evaluate(sum, c(2, 4, 6)) should evaluate to 12
#    2. evaluate(median, c(7, 40, 9)) should evaluate to 9
#    3. evaluate(floor, 11.1) should evaluate to 11

evaluate <- function(func, dat){
   func(dat)
}

evaluate(sum,c(2,4,6))

sum(c(2,4,6))

evaluate(sd,c(1.4, 3.6,7.9, 8.8)) #std for vector

evaluate(function(x){x+1},6) # function(x){x+1}=function

#using evaluate() along with an anonymous function to return the first element of the
#vector c(8, 4, 0).

evaluate(function(x){
  x[1]
},c(8,4,0)
)      

evaluate(function(x){
  x[3]
},c(8,4,0))
                                #same,  reture last element of vector
evaluate(function(x){
  x[length(x)]
},c(8,4,0))

```

##paste function   (same as SQL CONCAT() function)

```{r}
paste("Programming", "is", "fun!")

paste("a", "b", sep = ":")

# For example the expression `telegram("Good", "morning")` should evaluate to:
# "START Good morning STOP"

telegram <- function(...){
  paste("START",...,"STOP")
}

telegram("A","Z")
telegram("A","z","aaa","bbb")   #... =any strings you want


mad_libs <- function(...){
  # Do your argument unpacking here!
  args <- list(...)
  place <- args[["place"]]
  adjective <- args[["adjective"]]
  noun <- args[["noun"]]
  
  # Don't modify any code below this comment.
  # Notice the variables you'll need to create in order for the code below to
  # be functional!
  paste("News from", place, "today where", adjective, "students took to the streets in protest of the new", noun, "being installed on campus.")
}
mad_libs(place="home", adjective="nice", noun="me")
```
## binory operators

```{r}

"%mult_add_one%" <- function(left, right){ # Notice the quotation marks!
   left * right + 1
 }
4 %mult_add_one% 5  


```

binory operators with paste function

```{r}
# Write your own binary operator below from absolute scratch! Your binary
# operator must be called %p% so that the expression:
#
#       "Good" %p% "job!"
#
# will evaluate to: "Good job!"

"%p%" <- function(left,right){ # Remember to add arguments!
 paste(left,right)
}
"Good"%p%"job!"

"I" %p% "love" %p% "R!"
```

